The imprint of global magma oceans on exoplanet demographics

### 2023-03-27 src/tex/ms.tex
new Plato runs, redraw plots, update numbers

For a volume-limited sample, considering all host star spectral types, we find that a yield of \var{N_plato} planets enables a significant detection if the fraction of runaway greenhouse planets is larger than $\sim \var{platoMinfrgh}$ (see Fig.~\ref{fig:plato_fgrid}).
The minimum needed fraction rises to \var{platoMinfrghHundred} for $N = 100$.
For much smaller samples, even an optimistically strong signal can no longer be detected.

@@

%We now examine the value of a follow-up campaign to constrain planet masses with respect to the detectability of the runaway greenhouse threshold.
As can be seen in Fig.~\ref{fig:plato_fgrid}, the detectability is enhanced when radius constraints can be augmented with mass measurements: At unchanged sample size, the difference in Bayesian evidence can be up to an order of magnitude larger.
Consequently, we achieve a statistically significant detection with smaller samples or lower dilution factors $f_\mathrm{rgh}$.
A density-based survey of 100 targets is roughly equivalent to a radius-based survey of \var{N_plato} targets.
At $N=100$, pure radius measurements require $f_\mathrm{rgh} \gtrsim 0.4$ whereas bulk density measurements enable a detection from $f_\mathrm{rgh} \gtrsim 0.1$.

>>>>

For a volume-limited sample, considering all host star spectral types, we find that a yield of \var{N_plato} planets enables a significant detection if the fraction of runaway greenhouse planets is larger than $\sim \var{platoMinfrgh}$ (see Fig.~\ref{fig:plato_fgrid}).
The minimum needed fraction rises to \var{platoMinfrghHundred} for $N = 100$.
For much smaller samples, only a very optimistically strong signal is likely to be detected.

@@

%We now examine the value of a follow-up campaign to constrain planet masses with respect to the detectability of the runaway greenhouse threshold.
As can be seen in Fig.~\ref{fig:plato_fgrid}, the detectability is enhanced when radius constraints can be augmented with mass measurements: At unchanged sample size, the difference in Bayesian evidence can be up to an order of magnitude larger.
Consequently, we achieve a statistically significant detection with smaller samples or lower dilution factors $f_\mathrm{rgh}$.
A density-based survey of 100 targets is roughly equivalent to a radius-based survey of \var{N_plato} targets.
At $N=100$, pure radius measurements require $f_\mathrm{rgh} \gtrsim \var{platoMinfrghHundred}$ whereas bulk density measurements enable a detection from $f_\mathrm{rgh} \gtrsim \var{platoMinfrghHundred_rho}$.
